Import_MCData

### 2024-03-06 Code/Import_MCData.Rmd
Uncommented chunk
removed from library load 'data.table' -redundant

library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(data.table)
library(photobiologyWavebands)

@@

TargetFile <- "20220824_PICO_MC257_RUN86.csv"

@@

TargetDataMeta <- TargetDataMeta %>%
mutate(OD680 = if_else(Tube == 5, 0.005, OD680),
       OD720 = if_else(Tube == 5, 0.003, OD720))

@@

>>>>

library(tidyverse)
library(lubridate)
library(broom)
library(zoo)
library(photobiologyWavebands)

@@

TargetFile <- "20220701_PICO_MCMIX006_RUN80.csv"

@@

# TargetDataMeta <- TargetDataMeta %>%
# mutate(OD680 = if_else(Tube == 5, 0.005, OD680),
#        OD720 = if_else(Tube == 5, 0.003, OD720))

@@

TargetDataMetaFilter
